\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-15 public/paper/pyg4ometry.tex
Paper update

% part features
% part assembly
% physical volume
% logical volume
% daughter volume
% mother volume
% Reader
% scene
% API
% AST 
% BREP (not B-REP)
% region

@@

\begin{abstract}
Creating and maintaining computer readable geometries for use in Monte Carlo Radiation Transport (MCRT) simulations is a 
error prone and time consuming task. Simulating a system often requires geometry from different sources and modelling 
environments, including a range of MCRT codes and Computer-aided Design (CAD) tools. \PYGEOMETRY{} is a Python library 
that enables users to rapidly create, manipulate, display, read and write Geometry Description Markup Language (GDML) based 
geometry used in simulations. \PYGEOMETRY{} provides import of CAD files to GDML tessellated solids, conversion of GDML geometry 
to FLUKA and conversely from FLUKA to GDML. The implementation of \PYGEOMETRY{} is explained in detail along with 
examples. The paper concludes with a complete example using most of the \PYGEOMETRY{} features and a discussion of 
extensions and future work.
\end{abstract}

@@

\section{Quality assurance}
The source and manual code for \PYGEOMETRY{} is stored in a git repository (\url{https://bitbucket.org/jairhul/pyg4ometry}), 
where a public issue tracker for users is hosted to report problems or bugs with the code. The manual is created using Sphinx a 
Python documentation generator. \PYGEOMETRY{} uses mature packages available for Python as dependencies. 
\PYGEOMETRY{} has  two submodules that require compilation \pyinline{pyg4ometry.pycsg} and \pyinline{pyg4ometry.pycgal} 
in C/C++. \PYGEOMETRY{}, package dependencies and extensions are installed using \pyinline{setuptools}. All aspects of 
\PYGEOMETRY{} are routinely checked using unit tests, of which 543 tests are available for the code, which have 84\% coverage. 
The unit tests also serve as minimal examples to help users understand the code operation.

>>>>

% Python
% part features
% part assembly
% physical volume
% logical volume
% daughter volume
% mother volume
% Reader
% scene
% API
% AST 
% BREP (not B-REP)
% region

@@

\begin{abstract}
Creating and maintaining computer readable geometries for use in Monte Carlo Radiation Transport (MCRT) simulations is a 
error prone and time consuming task. Simulating a system often requires geometry from different sources and modelling 
environments, including a range of MCRT codes and Computer-aided Design (CAD) tools. \PYGEOMETRY{} is a Python library 
that enables users to rapidly create, manipulate, display, read and write Geometry Description Markup Language (GDML) based 
geometry used in simulations. \PYGEOMETRY{} provides import of CAD files to GDML tessellated solids, conversion of GDML geometry 
to FLUKA and conversely from FLUKA to GDML. The implementation of \PYGEOMETRY{} is explained in detail along with small  
examples. The paper concludes with a complete example using most of the \PYGEOMETRY{} features and a discussion of 
extensions and future work.
\end{abstract}

@@

\section{Quality assurance}
The source and manual code for \PYGEOMETRY{} is stored in a git repository (\url{https://bitbucket.org/jairhul/pyg4ometry}), 
where a public issue tracker for users is hosted to report problems or bugs with the code. The manual is created using Sphinx a 
Python documentation generator (\url{Monte Carlo Radiation Transport (MCRT)}). \PYGEOMETRY{} uses mature packages 
available for Python as dependencies. \PYGEOMETRY{} has  two submodules that require compilation \pyinline{pyg4ometry.pycsg} 
and \pyinline{pyg4ometry.pycgal} in C/C++. \PYGEOMETRY{}, package dependencies and extensions are installed using 
\pyinline{setuptools}. All aspects of \PYGEOMETRY{} are routinely checked using unit tests, of which 543 tests are available 
for the code, which have 84\% coverage. The unit tests also serve as minimal examples to help users understand the code operation.
